\documentclass[12pt, oneside, a4paper]{article}
\usepackage{graphicx}
\usepackage{ifpdf}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
\title{LocusEqu Project. Final Report.}
\author{Sergio Arbeo}\date{}\maketitle

\section{Brief introduction.}

In my humble opinion, LocusEqu has achieved some pretty impressive
results in its current state. However, its limitations are more important than 
its current features.\\

In this paper, implementation, features and limitations will be
discussed, as well as some guidelines for overcoming some of the
limitations.

\section{Implementation.}

LocusEqu classes can be found under geogebra.kernel.locusequ and
geogebra.kernel.locusequ.arith packages.\\

LocusEqu distinguish two types of AlgoElements and creates two
different kinds of objects. Some AlgoElements are considered
EquationElements, like AlgoJoinPoints, and other are considered
EquationRestrictions, like AlgoPointOnPath. The main difference is
that EquationElements does not creates any restrictions, while
EquationRestriction does.

\subsection{Scope}

One of the main pillars of LocusEqu is EquationScope.This class works
just as a variable scope in any programming language but way more
simple.\\

It contains two different scopes, one for points, relating GeoPoints
to EquationPoints; and another one relating GeoElements to
EquationElements. Both scopes work as maps and can create a proper
value given the key. The algorithm for creating a new EquationPoint
relies on a simple if with a few conditions, only one of them a bit
complicated. On the other hand, the algorithm for creating new
EquationElements is a bit more complicated since it uses a parser, for
lack of a better term, explained in the next subsection.

\subsection{Parsers}
\label{ss:Parsers}

There are two parsers in LocusEqu: EquationParser and
EquationRestrictionParser. Both share the design, so only the latter
will be explained.\\

EquationRestrictionParser contains a static Map from String to
EquationRestrictionBuilder. EquationRestrictionBuilder is an interface
containing only one method that returns an EquationRestriction from an
AlgoElement and an EquationScope. Keys are obtained from AlgoElements'
getClassName method.\\

Those AlgoElements considered EquationElements retrieve the
EquationNullRestrictionBuilder only instance. This object retrieves an
EquationNullRestriction, which only generates empty EquationList.\\

On the other hand, those AlgoElements considered to be
EquationRestrictions retrieve an anonymous EquationBuilder that
retrieves a proper EquationRestriction instance.

\subsection{EquationAuxiliarElement}

Any class implementing the empty interface EquationAuxiliarElement has
no correspondence with any GeoElement.\\

\subsection{EquationPoints}

There are three basic subclasses of EquationPoint: EquationFreePoint,
EquationDependentPoint and EquationSpecialSymbolicPoint. These
subclasses are already explained in the wiki, so I will skip any
explanation.\\

EquationNormalPoint, EquationPointVectorPoint and EquationUnitaryPoint
are used for creating a normal vector, applying a vector to a point
and creating a unitary vector. They all are auxiliar elements.\\

EquationMidpoint is obviously used for midpoints.\\

SymbolicVector extends EquationPoint too.

\subsection{EquationElements}

There are three abstract classes that extend EquationElement. They are
EquationGenericConic, EquationGenericLine and
EquationGenericPolygon.\\

These three classes can produce a restriction given a few basic data.

\subsubsection{EquationGenericConic}

EquationGenericConic needs an EquationExpression matrix, similar to
the one used by GeoGebra. Subclasses need to implement computeMatrix()
void method, which needs to call matrix setter at some point.\\

EquationGenericConic also hold all polar lines requested in a hash.

\subsubsection{EquationGenericLine}

EquationGenericLine needs a start point and a vector. The latter can
be given either as a SymbolicVector or as the equation parameters A, B
and C, calling getVectorFromABC method later to get a proper
SymbolicVector. Take a look at EquationDiameterLine for working with
equation coefficients.

\subsubsection{EquationGenericPolygon}

Working with EquationGenericPolygon is even easier than working with
EquationGenericLine, it only needs a GeoSegmentInterface array to
work.

\subsection{EquationExpression}

The better way for building an EquationExpression is using the static
methods in EquationBuilderHelpers (just use import static, for
simplicity's sake).\\

Every function is documented (even just by its name and args), so do
not hesitate to use them.

\subsection{EquationTranslator}

Implementing a translator from EquationExpression to T (T understood
as a Java generic parameter) is as easy as extend the abstract class
EquationTranslator<T>. Its abstract methods are simple to implement
(usually, take a look at sqrt method in ExpressionToJasTranslator in
order to know what I am talking about). LocusEqu use structural
induction to use the translator, so you only need to worry about the
basic and inductive steps.

\section{Known problems}

Even if LocusEqu can work out a lot of examples, it has a lot of
limitations but, luckily, some of them can be solved in near future.\\

\subsection{AlgoElements whose complexity is not bounded}

LocusEqu algorithm does take time when locus is a bit complex. Current
AlgoElements implementation only gives two choices for updating the
view. Both of them updates the view in real time, which is not useful
when computing the algo takes more than a few milliseconds. A lagged
user experience is not a good one, and some solution must be
implemented.

\subsubsection{Solution}

Even if an algebraic solution can be implemented, it would rise
complexity and can make LocusEqu almost useless. The suggested
solution consists on only update LocusEqu after user has stopped
moving elements around.
\end{document}
